{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-23 brains-protocol.tex
4.1 minor

\medskip
The results for this observable, gathered on Fig.~\ref{fig:feature-susceptibilities}, first show an obvious strong effect of Word frequency: the more frequent a word, the less likely it is to attract substitutions. Indeed, susceptibility goes from nearly 0.4 for low-frequency words down to 0 for very high-frequency words.

Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}
This class of words corresponds to \TB{highly specialized words? domain-specific? a hard limit on too complicated words?}

>>>>

\medskip
Results are gathered on Fig.~\ref{fig:feature-susceptibilities}. They first show an obvious strong effect of Word frequency: the more frequent a word, the less likely it is to attract substitutions. Indeed, susceptibility goes from nearly 0.4 for low-frequency words down to 0 for very high-frequency words. As a reminder, this value of 0.4 means that, this kind of low-frequency words, when present in a quote undergoing a substitution, are indeed the one being substituted 40\% of the time on average.

Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}
This class of words corresponds to \TB{highly specialized words? domain-specific? a hard limit on too complicated words?}
